\documentclass[letterpaper]{article}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Package loading
\usepackage[letterpaper,left=6mm,right=6mm,top=2mm,bottom=0mm]{geometry}
%\usepackage[letterpaper,left=12mm,right=12mm,top=8mm,bottom=9mm]{geometry}
\usepackage{graphicx,nopageno}
\usepackage[compact]{titlesec}
\usepackage{hyperref}
\hyphenation{LabVIEW}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Custom commands
\makeatletter
\newcommand*{\compress}{\@minipagetrue}
\makeatother

\newcommand{\rsection}[4]{\noindent\large
\hspace{5pt}\textbf{#1} #2 \hfill \textbf{#3}\\
\parbox{.95\textwidth}{#4}
}

\newcommand{\risection}[4]{\noindent\large
\textbf{#1} #2 \hfill \textbf{#3}\\
\parbox{.95\textwidth}{
\begin{ritemize}
#4
\end{ritemize}
}
}

\newenvironment{ritemize}{
\compress\vskip 5pt
\begin{itemize}
  \setlength{\itemsep}{-1pt}
  \setlength{\partopsep}{-5pt}
  \setlength{\parsep}{0pt}
  \setlength{\topsep}{0pt}
  }
  {
  \end{itemize}
  }

\renewcommand{\labelitemi}{$-$}

\newenvironment{absolutelynopagebreak}
  {\par\nobreak\vfill\penalty0\vfilneg
   \vtop\bgroup}
  {\par\xdef\tpd{\the\prevdepth}\egroup
   \prevdepth=\tpd}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Header
\begin{document}\raggedbottom\hrule\medskip\hfill
\raisebox{-1.5mm}{\Huge Jeremy Silver}
\hfill
\begin{tabular}{lr}
235 Berry St Apt 508 & \href{https://linkedin.com/in/jeremysilvertongue}{linkedin.com/in/jeremysilvertongue}\\
San Francisco, CA. 94185 & \href{https://github.com/jeremysilvertongue}{github.com/jeremysilvertongue}\\
(503)-502-2958 & \href{https://www.hackerrank.com/JeremySilver}{hackerrank.com/jeremysilver}\\
\href{mailto:jeremysilvertongue@gmail.com}{jeremysilvertongue@gmail.com} & \href{http://stackoverflow.com/users/679647/jeremy-silver}{stackoverflow.com/users/679647}
\end{tabular}
\medskip


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Experience


\hrule\bigskip
\risection{Software Engineer}
{Stripe, San Francisco, California.}
{June 2017--September 2018}
{
\item As a member of the streaming data infrastructure team, decomposed a monolithic event handling system into loosely coupled scheduler and workers, communicating via Kafka.
\item Added Proto3 schemas and a gRPC interface to Stripe's streaming/batch computation platform.
\item Wrote tooling and microservices for filtering, searching, archiving, and replaying Kafka streams.
\item Standardized metric collection across the team's services, while migrating monitoring and alerting to SignalFx. Designed new dashboards for system maintenance and incident investigation.
}


\risection{Android Course Developer}
{Udacity, Mountain View, California.}
{April 2014--January 2017}
{
\item Created online courses that attracted tens of thousands of students. Responsible for all stages of course creation: outlining, scripting, creating sample code and exercises, and finally appearing on camera.
\item Instructor of \href{https://www.udacity.com/course/gradle-for-android-and-java--ud867}{\textsl{Gradle for Android and Java}}, \href{https://www.udacity.com/course/2d-game-development-with-libgdx--ud405}{\textsl{2D Game Development with libGDX}}, and \href{https://www.udacity.com/course/how-to-make-a-platformer-using-libgdx--ud406}{\textsl{How to Make a Platformer Using libGDX}}. Contributed scripts and sample code to \href{https://www.udacity.com/course/new-android-fundamentals--ud851}{\textsl{Developing Android Apps}} and \href{https://www.udacity.com/course/android-basics-networking--ud843}{\textsl{Android Basics: Networking}}, made in partnership with Google.
\item Developed a sample code delivery system that allows instructors to create and maintain an idealized Git history for students to follow along with.
}

\risection{Machine Vision Intern}
{Allion USA, Portland, Oregon.}
{January 2014--April 2014}
{
\item Built stages of a machine vision pipeline for real-time processing of high speed camera output.
\item Invented a class of ternary/n-ary codes with desirable Hamming distance properties.
}

\risection{Scientific Applications Developer}
{Apple, Portland, Oregon.}
{June 2011--August 2013}
{
\item Developed novel algorithms as an intern with the Advanced Computation Group in the fields of sound compression, image compression, image enhancement, machine vision, and error correction coding.
\item Created 3D scanning and printing laboratory and wrote tools for interactive markup of 3D meshes.
% \item Coinvented, prototyped, and wrote patent documentation for a novel image magnification algorithm. Collaborated on a real-time OpenCL implementation of the algorithm.
}

\risection{Senior Reactor Operator}
{Reed Research Reactor, Portland, Oregon.}
{August 2009--May 2011}
{
\item As Requalification Supervisor, created and administered written and practical exams to the staff, gave training and requalification lectures, and founded an enrichment lecture series.
\item Performed and supervised reactor power changes,  control rod and fuel inspections, thermal power calibration, refueling operations, and neutron activation analysis experiments.
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Education
%\hrule
%\bigskip
\risection{Reed College}
{BA, Physics. Portland, Oregon.}
{May 2011}
{
\item Thesis on the use of numerical differential equation solving and genetic algorithms to simulate and optimize human movement.
%\item Course work in calculus, linear and abstract algebra, scientific computation, electrodynamics, elementary particles, as well as classical, quantum, thermal, and solid-state physics.
%\item Laboratory work in electronics, optics, kinematics, electromagnetism, and machine tooling.
\item Projects included measuring the temperature dependence of diode reverse bias leakage current, improvised synthesis of fullerenes using a welding power supply, and creation of an interactive computer model simulating the interaction and collision of charged particles.
}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% skills
\hrule\bigskip
\risection{Skills}
{}
{}
{
\item Deep experience with Scala, Python, and Java. Professional experience in C++, Go, Ruby, and Bash.
\item AWS, Kafka, NSQ, Consul, Apache Storm, MongoDB, Protobuf/gRPC, Splunk, SignalFx, and Datadog.
\item Git, Mercurial, Gradle, Maven, SBT, and Bazel.
\item Android App development, libGDX, Arduino, SKLearn, OpenCV, Mathematica, MATLAB, and \LaTeX.
}
\hrule

\end{document}



\risection{Student Engineer}
{US Nuclear Regulatory Commission, Washington DC.}
{June--August 2009}
{
\item Wrote and contributed to numerous reports and white papers
  including an assessment of the safety hazards associated with
  the aqueous homogeneous reactor type and its viability for producing
  radiopharmaceutical precursors.
\item Composed the charter and communication plan of a working group addressing a radiopharmaceutical shortage.
\item Assisted in inspections of the NIST and UNM research reactors
  and contributed to the relicensing safety evaluation report of the
  latter.
}

\risection{Wet-deck Operator}
{MicroSemi PPG, Bend, Oregon.}
{June--August, 2008}
{
\item Ran five production lines performing chemical etching and stripping processes involved in microchip fabrication.
}

\risection{Camp Counselor/Technical Theater Assistant}
{Young Musicians and Artists, Salem, OR.}
{July, 2006}
{
\item Assisted in teaching campers theatrical lighting, rigging, and
 sound design.
\item Established safety culture among students spending many hours on
 up to 30' ladders.
\item Forged a rabble of middle-schoolers into an effective team.
}

\risection{Community Theater}
{2nd Street Theater and Cascades Theatrical Company, Bend, Oregon.}
{2004--2007}
{
\item Performed with local theatrical companies in five productions of
  20 performances each. Roles included John in \textsl{The Lion in
    Winter}, the Dog in \textsl{Blind Willie and the Talking Dog}, and an
  ensemble member in  \textsl{Jesus Christ Superstar}.
\item Ran lights and performed other technical work for a further two
  shows; \textsl{Chicago} and \textsl{Sweet Charity}.
}

\risection{Member of Debate Team}
{Summit High School, Bend, Oregon.}
{2005--2007}
{
\item Attained membership with special distinction in the National
  Forensic League.
\item Competed in the 2006 NFL National Tournament in public forum debate
  and the 2007 National Tournament in international extemporaneous
  speaking.
}

\risection{High School Theater}
{Summit High School, Bend, Oregon.}
{2005--2007}
{
\item Performed in and built sets for three productions
  including \textsl{The Taming of the Shrew}.
\item Stepped in for a sick actor two weeks before opening night.
}


\rsection{Summit High School}
{Graduated with honors. Bend, Oregon.}
{June, 2007}
{
\begin{ritemize}
\item Advanced placement course work in physics, chemistry, biology,
  calculus, Spanish, European history, English language and
  composition, and US government.
\item Extracurricular activities include anchoring daily television
  news, GSA, Wikipedia club, weight training, lacrosse, cross country
  running, debate (including two national championships), and theater.
  \end{ritemize}
}


